### 2016-06-06 paper.tex
Add second paper prototype image
There was some ugly whitespace, and adding another image helped achieve balance.
Add screenshots from iteration 3
Remove blinded elements of accepted paper

% Is this blind or not?
\newtoggle{blind}
\toggletrue{blind}

@@

In order to explore the potentials within this genre,
we formed a team to conduct a design experiment and pilot study.
The team adopted a constructionist perspective~\citep{Papert2001},
that our understanding of the genre would be improved by engaging
with design, development, and evaluation---building prototypes
as a way to understand them.
We formed a partnership with \textit{[omitted for blind review]}, 
a non-lending branch that 
provides community, training, and technology services in a
low socioeconomic area of our city.
The youth patrons of the library tend to be 4rd--6th grade 
``latchkey kids'' who 
see the library as an after-school destination to visit with friends, 
participate in programs, and access technology.

@@

Our team comprised ten undergraduate students and one faculty mentor.
The students' majors included Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation), and 
each earned three credit-hours during a fifteen-week
semester,
working together in a studio space for two hours each Monday, Wednesday,
and Friday.
% In future version, cite the TOCE paper
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address problems of analog implementations.

The team proceeded with an incremental and
iterative approach to game design and development.
The team used a design log to record design decisions~\citep{Cook2011},
and each iteration
produced an executable release in accordance with best practices of
agile software development~\citep{Cockburn2006};
figures~\ref{fig:screenshots} and~\ref{fig:paper-prototype} demonstrate
artifacts from the design and development process.
Each iteration was tested at
\textit{[the library branch]}, providing valuable feedback to the
team. 
In addition to paper prototypes, the team 
developed software-based prototypes using JavaFX, PlayN, and Polymer, 
all of which allow for HTML5 Web deployment.
Game images and stories were inspired by the team's research on monsters
from world cultures, which included both research sources
(such as \citet{Cohen1996}) and children's books (especially
\citet{Steer2008} and \citet{Stowell2013}).
The team also consulted with local university experts on
games, monsters, world cultures, and literacy.
Each iteration concluded with a retrospective
meeting, which provided an opportunity for the
team's reflective improvement~\citep{Kerth2001,Schon1984}.

@@

\begin{figure}
\centering
\includegraphics[width=\figwidth]{paper-prototype}
\caption{Paper prototype from Iteration 3}
\label{fig:paper-prototype}
\end{figure}

@@

While the visual design and overall rules structure remained stable
throughout the iterations of our experiment, the encounter stories
themselves changed dramatically.
Our target audience required that both stories and gameplay 
had to be much shorter than in other games that we analyzed,
our final version having a 175-character limit.
\textit{[Library branch]} is a high-distraction environment,
where our game competes for attention against both formal and informal
activities. The game takes approximately fifteen minutes to complete,
which we found to be a good balance of keeping players' attention,
making them curious to play again,
and fitting within our limited means for producing content.

@@

\section{Acknowledgments}
\textit{The team, organizational, and community partner
  acknowledgments are hidden for blind review.}

>>>>

% Is this blind or not?
\newtoggle{blind}
\togglefalse{blind}

@@

In order to explore the potentials within this genre,
we formed a team to conduct a design experiment and pilot study.
The team adopted a constructionist perspective~\citep{Papert2001},
that our understanding of the genre would be improved by engaging
with design, development, and evaluation---building prototypes
as a way to understand them.
We formed a partnership with Connection Corner, 
a non-lending branch of Muncie Public Library~(Muncie, Indiana, USA) that 
provides community, training, and technology services in a
low socioeconomic area of our city.
Many youth patrons of the library are 4rd--6th grade 
``latchkey kids'' who 
see the library as an after-school destination to visit with friends, 
participate in programs, and access technology.

@@

Our team comprised ten undergraduate students and one faculty mentor.
The students' majors included Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation), and 
each earned three credit-hours during a fifteen-week
semester,
working together in an academic studio~\citep{Gestwicki2016}
for two hours each Monday, Wednesday, and Friday.
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address problems of analog implementations.

The team proceeded with an incremental and
iterative approach to game design and development.
The team used a design log to record design decisions~\citep{Cook2011},
and each iteration
produced an executable release in accordance with best practices of
agile software development~\citep{Cockburn2006};
figures~\ref{fig:screenshots} and~\ref{fig:paper-prototype} demonstrate
artifacts from the design and development process.
Each iteration was tested at
Connection Corner, providing valuable feedback to the
team. 
In addition to paper prototypes, the team 
developed software-based prototypes using JavaFX, PlayN, and Polymer, 
all of which allow for HTML5 Web deployment.
Game images and stories were inspired by the team's research on monsters
from world cultures, which included both research sources
(such as \citet{Cohen1996}) and children's books (especially
\citet{Steer2008} and \citet{Stowell2013}).
The team also consulted with local university experts on
games, monsters, world cultures, and literacy.
Each iteration concluded with a retrospective
meeting, which provided an opportunity for the
team's reflective improvement~\citep{Kerth2001,Schon1984}.

@@

\begin{figure}
\centering
\includegraphics[width=\figwidth]{paper-prototype}
\includegraphics[width=\figwidth]{paper-prototype-2}
\caption{Paper prototypes from Iteration 3}
\label{fig:paper-prototype}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\figwidth]{i3-shot1}
\includegraphics[width=\figwidth]{i3-shot2}
\caption{Screenshots from Iteration 3}
\label{fig:paper-prototype}
\end{figure}

@@

While the visual design and overall rules structure remained stable
throughout the iterations of our experiment, the encounter stories
themselves changed dramatically.
Our target audience required that both stories and gameplay 
had to be much shorter than in other games that we analyzed,
our final version having a 175-character limit.
Connection Corner is a high-distraction environment,
where our game competes for attention against both formal and informal
activities. The game takes approximately fifteen minutes to complete,
which we found to be a good balance of keeping players' attention,
making them curious to play again,
and fitting within our limited means for producing content.

@@

\section{Acknowledgments}
The authors acknowledge the contributions of other team members who
created \textit{Traveler's Notebook}: 
Nicholas Boyer,
Ashley Cox,
Jessica Lohse,
Jack McGinnis,
Lucas Miller,
Joshua Schoen,
Brennan Wade,
and Caleb Woods.
Jennifer Grouling and Joyce Huff also contributed to our design experiment.
We are grateful for the cooperation of Muncie Public Library, especially
from Rebecca Parker and Stuart Cotton 
This work was internally supported by the College of Sciences and
Humanities and the Computer Science Department at Ball State University.
